Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-08-06 paper/paper.Rmd
some quick edits in Discussion section

There are various variables influencing the partitioning method choice for an environmental dataset:

- Do natural groupings exists in the data? Examples include agricultural fields, forest stands, lithology types, etc.
- How dense are the observations scattered both in space and time?
  The closer observations are in space and/or time, the more similar they are, and hence the greater is the effect of spatio-temporal autocorrelation.
- Are some of the predictor variables under consideration known to be strongly autocorrelated such as air temperature or precipitation?

@@

<!-- group level CV vs custom CV -->
\pkg{mlr3spatiotempcv} supports two factor-based partitioning schemes: "group-level resampling" and "custom resampling".
Both are similar in that they require external user input for partition creation, i.e. a factor variable which assigns all observations into a distinct group.
The idea of "custom resampling" is that each group becomes a test set in the CV.
By contrast, "group-level resampling" methods resample these initial groups: for example, users can supply an integer value to an argument named `fold` in the LLO method (e.g. `5L`) which combines the initial groups (e.g. $n = 20$) into their final fold-level partitions, which would result in four groups per partition [@meyer2018].
The important point is that observations from within one group will either be assigned to the train or test set and never be split up.
"Group-level resampling" can be, in contrast to "custom resampling", repeated multiple times because multiple different aggregations are possible in theory.
However, it also requires the number of initial groups to be substantially higher than the number of folds so that a sensible aggregation is possible in the first place.

@@

<!-- env block: hard to decide which variable to use for clustering -->
<!-- env block: more than one variable may lead to unforeseeable results -->
Method `"spcv_env"` is complicated to use in that it requires the user to limit the clustering to one or more variables [@blockCV].
This implies that only this/these variable(s) suffer from autocorrelation and others are ignored.
However, it is not possible to estimate how much a single variable accounts for the autocorrelation in the data and the same applies for estimating the influence of the non-accounted variables which might add substantial bias to the CV.

>>>>

There are various factors that might influence the choice of a partitioning method:

- Do natural groupings exists in the data? Examples include multi-level sampling designs, land management units, or other characteristics of the study area or sampling design that may induce random effects.
- How dense are the observations scattered both in space and time?
  The closer observations are in space and/or time, the more similar they are, and hence the greater is the effect of spatio-temporal autocorrelation on performance estimates.
- Are some of the predictor variables under consideration known to be strongly autocorrelated such as air temperature or precipitation at the regional level?

@@

<!-- group level CV vs custom CV -->
\pkg{mlr3spatiotempcv} supports two factor-based partitioning schemes: "group-level resampling" and "custom resampling".
Both are similar in that they require external user input for partition creation, i.e. a factor variable which assigns all observations into a distinct group.
The idea of "custom resampling" is that each group becomes a test set in the CV (leave-one-group-out CV).
By contrast, "group-level resampling" methods resample these initial groups: for example, users can supply an integer value to an argument named `fold` in the LLO method (e.g. `5L`) which combines the initial groups (e.g. $n = 20$) into their final fold-level partitions, which would result in four groups per partition [@meyer2018].
The important point is that observations from within one group will either be assigned to the train or test set and never be split up.
"Group-level resampling" can be, in contrast to "custom resampling", repeated multiple times because multiple different aggregations are possible in theory.
However, it also requires the number of initial groups to be substantially higher than the number of folds so that a sensible aggregation is possible in the first place.

@@
